\documentclass[pdftex,12pt,a4paper]{article}

% --- Preamble ---
\usepackage{graphicx}
\usepackage[margin=2.5cm]{geometry}
\usepackage{breakcites}
\usepackage{indentfirst}
\usepackage{pdflscape}
\usepackage{float}
\usepackage[cmex10]{amsmath}
\usepackage{multirow}
\usepackage{fancyvrb}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{array}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={BLG 475E Term Project Report - Final Submission},
    pdfpagemode=UseOutlines,
}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{color}

% Code listing settings
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}
\lstset{style=mystyle}

% --- Settings ---
\renewcommand{\refname}{REFERENCES}
\linespread{1.3}

\begin{document}

% --- Title Page ---
\begin{titlepage}
\begin{center}
\textbf{}\\
\textbf{\Large{ISTANBUL TECHNICAL UNIVERSITY}}\\
\vspace{0.5cm}
\textbf{\Large{COMPUTER ENGINEERING DEPARTMENT}}\\
\vspace{4cm}
\textbf{\Large{BLG 475E\\ SOFTWARE QUALITY AND TESTING\\ TERM PROJECT REPORT --- FINAL SUBMISSION\\ (PHASE 1 + PHASE 2)}}\\
\vspace{4cm}
\begin{table}[ht]
\centering
\Large{
\begin{tabular}{lcl}
\textbf{COURSE}     & : & BLG 475E \\
\textbf{LECTURER}   & : & Sultan \c{C}o\u{g}ay \\
\textbf{TERM}       & : & 2025--2026 Spring \\
\end{tabular}}
\end{table}
\vspace{1.5cm}
\begin{table}[ht]
\centering
\Large{
\begin{tabular}{lcl}
\textbf{Mustafa Eren KO\c{C}}    & : & 150190805 \\
\textbf{Onat Bar{\i}\c{s} ERCAN} & : & 150210075 \\
\end{tabular}}
\end{table}
\vspace{2.8cm}
\textbf{\Large{SPRING 2026}}
\end{center}
\thispagestyle{empty}
\end{titlepage}

% --- Table of Contents ---
\thispagestyle{empty}
\addtocontents{toc}{\contentsline {section}{\numberline {}FRONT COVER}{}}
\addtocontents{toc}{\contentsline {section}{\numberline {}CONTENTS}{}}
\setcounter{tocdepth}{4}
\tableofcontents
\clearpage

% --- Main Content Start ---
\setcounter{page}{1}
\pagenumbering{arabic}

% =============================================================
% INTRODUCTION
% =============================================================
\section{INTRODUCTION}
\label{sec:introduction}

This is the final combined submission report for the BLG~475E Software Quality and Testing term project at Istanbul Technical University. It consolidates Phase~1 (warm-up) and Phase~2 (extension) of the project into a single coherent document. The project investigates how two publicly available, code-oriented Large Language Models (LLMs) --- \texttt{Qwen2.5-Coder-1.5B-Instruct} and \texttt{DeepSeek-Coder-1.3B-Instruct} --- behave when asked to generate Java code and tests, first on isolated HumanEval-X prompts (Phase~1) and then on a composite class called \texttt{BookScan} that integrates three of those prompts (Phase~2).

Phase~1 establishes the methodology, the toolchain and the baseline measurements. Both LLMs reach 30 / 30 base-test success on a balanced 30-prompt subset of the HumanEval-X Java corpus \cite{humaneval}; the improved suites raise aggregate JaCoCo branch coverage from 96.09\,\% / 98.46\,\% (Qwen / DeepSeek) on the base suites to 98.44\,\% / 100.00\,\%, and every (task, model) pair carries at least one hand-crafted \texttt{improvedMutation\ldots} JUnit method.

Phase~2 lifts the helpers behind three Phase~1 tasks --- Java/18 (\texttt{howManyTimes}), Java/23 (\texttt{strlen}) and Java/27 (\texttt{flipCase}) --- into a single composite \texttt{BookScan} class that must determine how many words of a requested length appear in a text and on which lines they appear, and how many times a requested whole word appears across lines. We then compare four LLM-generated implementations (two prompt strategies $\times$ two models) against a manually selected final implementation and validate the final implementation through a Maven build with Surefire, JaCoCo and PITest. The final \texttt{BookScan} passes 18 / 18 integration and regression tests, reaches 100\,\% branch and line coverage and records an 84.95\,\% PITest mutation score. The most important Phase~2 finding is that explicit prompt contracts move both models from $\sim\!\!33\!-\!\!44\,\%$ pass-rate up to $\sim\!\!94\,\%$ on the same suite, while switching between the two models inside a fixed prompt strategy moves the pass-rate by no more than two test cases.

\subsection{Project Objectives}

The combined Phase~1 + Phase~2 objectives are:
\begin{itemize}
    \item Select two publicly available code-oriented LLMs that can be deployed locally (no paid APIs) and use them under a semi-agentic workflow that records every artefact.
    \item Select 30 HumanEval-X Java prompts balanced across easy / moderate / hard categories and use them as the Phase~1 corpus.
    \item Generate Java solutions with both LLMs, convert the dataset reference tests into JUnit~6, and measure branch coverage with JaCoCo.
    \item Improve the generated suites using test-smell auditing, equivalence-class partitioning, boundary-value analysis and hand-crafted mutation guards.
    \item Reuse the helpers behind Java/18, Java/23 and Java/27 to build a composite \texttt{BookScan} class in Phase~2 and write integration tests for it.
    \item Compare the LLMs under an \emph{original combined prompt} and an \emph{edited combined prompt} that adds explicit integration contracts, and validate the final implementation through Maven, JaCoCo and PITest.
    \item Survey five recent peer-reviewed papers on LLM-based test generation, hand-written without LLM assistance.
    \item Produce this final combined report (at least eight pages) that documents methodology, results, threats to validity and the literature review for both phases.
\end{itemize}

\subsection{Report Structure}

Section~\ref{sec:phase1-method} summarises the Phase~1 methodology (LLM selection, semi-agentic workflow, prompt selection, test improvement, mutation guards). Section~\ref{sec:phase1-results} presents the Phase~1 measured results. Section~\ref{sec:phase2-method} introduces the \texttt{BookScan} class, the Maven build and the original-vs-edited prompt comparison. Section~\ref{sec:phase2-challenges} documents the Phase~2 technical challenges (PITest under non-ASCII workspace paths, JaCoCo / PITest coexistence). Section~\ref{sec:phase2-results} reports the Phase~2 measured results: prompt-comparison outcomes, JaCoCo coverage and PITest mutation score. Section~\ref{sec:discussion} discusses both phases together. Section~\ref{sec:literature} contains the five-paper literature review. Section~\ref{sec:conclusion} concludes the project. Acknowledgement, references and appendices follow.

% =============================================================
% PHASE 1 METHODOLOGY (CONDENSED)
% =============================================================
\section{PHASE 1 METHODOLOGY}
\label{sec:phase1-method}

\subsection{LLM Selection and Workflow}

We chose a \textbf{semi-agentic} workflow: every transition between steps remains observable, each step writes its inputs and outputs into the repository, and a fully autonomous loop is not necessary because the local \texttt{llama.cpp} runtime would have required additional infrastructure that is unrelated to the research question.

The two selected models are:
\begin{itemize}
    \item \texttt{Qwen/Qwen2.5-Coder-1.5B-Instruct}, deployed as \texttt{Qwen2.5-Coder-1.5B-Instruct-GGUF}.
    \item \texttt{deepseek-ai/deepseek-coder-1.3b-instruct}, deployed as \texttt{DeepSeek-Coder-1.3B-Instruct-GGUF}.
\end{itemize}
Both models are loaded into the same local \texttt{llama.cpp} runtime with identical sampling parameters; the only varying factor between two paired experiments is the model itself. Both models are public, code-oriented, instruction-tuned and small enough ($<$8\,GB) to run on a student laptop. The Phase~1 pipeline is driven by PowerShell~7 and Python~3.11 scripts and re-runs end-to-end on every push via GitHub Actions (\texttt{.github/workflows/phase1-ci.yml}).

\subsection{Prompt Selection and Difficulty Distribution}

We selected exactly 30 prompts from the HumanEval-X Java corpus and recorded the rationale for each in \texttt{Phase1/data/selected\_prompts.csv}. The selection covers multiple input/output styles (numeric scalars, lists, strings, mixed types) and is balanced across difficulty categories:

\begin{table}[H]
\centering
\caption{Phase 1 difficulty distribution.}
\label{tab:difficulty}
\begin{tabular}{lc}
\toprule
\textbf{Difficulty} & \textbf{Count} \\
\midrule
easy     & 10 \\
moderate & 10 \\
hard     & 10 \\
\midrule
\textbf{total} & \textbf{30} \\
\bottomrule
\end{tabular}
\end{table}

Three of the selected prompts (Java/18 \texttt{howManyTimes}, Java/23 \texttt{strlen}, Java/27 \texttt{flipCase}) are explicitly retained because Phase~2 lifts their helpers into a composite \texttt{BookScan} class. The full task list is reproduced in Appendix~\ref{app:prompts}.

\subsection{Code Generation and Base Test Conversion}

For every selected prompt, the verbatim HumanEval-X declaration is sent to the model. The course brief forbids editing the prompt itself, so the only post-processing applied is structural normalization: removing Markdown fences, stripping a re-stated prompt that some models echo, and dropping malformed fragments that would prevent compilation. Semantic normalization is forbidden at this step; if a normalized solution still fails the base test, that failure is recorded and the repair happens in the refactoring loop, not silently in the normalizer.

The dataset's \texttt{Main.java} reference test is also re-encoded as a JUnit~6 \texttt{DatasetBaseTest.java} so that JaCoCo can be attached.

\begin{lstlisting}[language=Java, caption=Header block prepended to every generated solution and test]
/* @Authors
 * Student Names: Mustafa Eren KOC, Onat Baris ERCAN
 * Student IDs: 150190805, 150210075
 */
\end{lstlisting}

\subsection{Test Improvement and Hand-Crafted Mutation Guards}

For every (task, model) pair an improved JUnit suite \texttt{DatasetImprovedTest.java} is authored on top of the base test. The improvement comes from three orthogonal sources:
\begin{itemize}
    \item A \emph{test-smell audit} against the Phase~1 checklist that catches happy-path-only suites, conditional logic in tests, missing boundary cases and assertion roulette.
    \item An \emph{equivalence-partitioning} document with valid classes, invalid classes and boundary conditions; rows that are not already covered by the base test become the driver for at least one new \texttt{@Test} method.
    \item Hand-crafted \emph{mutation guards}: each improved suite has at least one \texttt{improvedMutation\ldots} method that fails if a specific operator-level mutation (ROR, AOR, LCR, UOI, BND, SBR, RV, NPE, EXC) is introduced into the solution. Phase~1 forbids automated mutation tooling, so the guards are encoded as JUnit assertions.
\end{itemize}

\begin{table}[H]
\centering
\caption{Hand-crafted mutation operators exercised in Phase 1.}
\label{tab:mutation-catalogue}
\begin{tabular}{p{0.07\linewidth}p{0.25\linewidth}p{0.55\linewidth}}
\toprule
\textbf{Op} & \textbf{Family} & \textbf{Representative Phase 1 use} \\
\midrule
ROR & Relational operator        & Java/3 balance check \verb|< 0| versus \verb|<= 0| \\
AOR & Arithmetic operator        & Java/2 \texttt{Math.floor} versus \texttt{(int)} truncation \\
LCR & Logical connector          & Java/9 short-circuit \verb|null  ||  size==0| \\
UOI & Unary operator insertion   & Java/31 negative-prime guard \\
BND & Boundary literal shift     & Java/25 / Java/36 numeric guards \\
SBR & Statement block removal    & Java/0 self-pair skip ($i == j$) \\
RV  & Return-value replacement   & Java/39 non-positive index \\
NPE & Null-argument replacement  & Applied to almost every I1 invalid class \\
EXC & Exception expectation flip & Java/11 unequal-length string inputs \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Refactoring Loop}

If a normalized solution fails the dataset base test, the workflow does not silently fix the code: it issues a refactoring prompt to the same model, attaches the failure log and the broken solution, and stores the resulting patch as the new solution. Seven tasks --- Java/10, Java/12, Java/17, Java/19, Java/23, Java/27, Java/39 --- needed exactly one refactoring round before reaching base-test success on at least one model; all seven were eventually fixed and now compile and pass on both models.

% =============================================================
% PHASE 1 RESULTS (CONDENSED)
% =============================================================
\section{PHASE 1 RESULTS}
\label{sec:phase1-results}

\subsection{Code Generation Outcomes}

\begin{table}[H]
\centering
\caption{Phase 1 code generation outcomes (after the refactoring loop).}
\label{tab:codegen-final}
\begin{tabular}{lcc}
\toprule
\textbf{Model} & \textbf{Compiled} & \textbf{Base tests passed} \\
\midrule
Qwen2.5-Coder-1.5B-Instruct-GGUF    & 30 / 30 & 30 / 30 \\
DeepSeek-Coder-1.3B-Instruct-GGUF   & 30 / 30 & 30 / 30 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Branch Coverage}

\begin{table}[H]
\centering
\caption{Phase 1 aggregate branch coverage (base versus improved).}
\label{tab:phase1-cov}
\begin{tabular}{lrrrrrr}
\toprule
& \multicolumn{3}{c}{\textbf{Base suite}} & \multicolumn{3}{c}{\textbf{Improved suite}} \\
\cmidrule(lr){2-4}\cmidrule(lr){5-7}
\textbf{Model} & Cov. & Total & \% & Cov. & Total & \% \\
\midrule
Qwen2.5-Coder-1.5B-Instruct-GGUF    & 123 & 128 & 96.09 & 126 & 128 &  98.44 \\
DeepSeek-Coder-1.3B-Instruct-GGUF   & 128 & 130 & 98.46 & 130 & 130 & 100.00 \\
\bottomrule
\end{tabular}
\end{table}

The two remaining Qwen-side misses are concentrated on Java/001 \texttt{separateParenGroups} and Java/006 \texttt{parseNestedParens}, where the Qwen-generated parser contains a private helper-exit branch that is not reachable through the public API under the dataset contract. We document these residual misses in Section~\ref{sec:discussion}.

\subsection{Hand-Crafted Mutation-Kill Status}

By construction, the improved suites kill 100\,\% of the hand-crafted Phase~1 mutants and the LLM-produced base suites kill 0\,\% of them. Phase~2 supplements this with PITest measurements on \texttt{BookScan} (Section~\ref{sec:phase2-results}).

\subsection{Model-Specific Behavioural Divergence}

For several Phase~1 tasks the two models produced semantically distinct implementations. Table~\ref{tab:divergence} lists the most informative examples; the improved suites carry different assertions for those tasks so that the suite documents what each LLM actually did.

\begin{table}[H]
\centering
\caption{Phase 1 tasks where Qwen and DeepSeek diverge on observable behaviour.}
\label{tab:divergence}
\begin{tabular}{p{0.10\linewidth}p{0.85\linewidth}}
\toprule
\textbf{Task} & \textbf{Behavioural disagreement} \\
\midrule
Java/2  & Qwen uses \texttt{Math.floor} for negative input; DeepSeek uses an \texttt{(int)} cast (which truncates toward zero, not toward $-\infty$). \\
Java/4  & Qwen returns \texttt{Optional.orElse(0.0)} on the empty-list case; DeepSeek divides by zero and returns \texttt{NaN}. \\
Java/19 & Qwen falls back to \texttt{indexOf == -1} when a token is not in the dictionary; DeepSeek calls \texttt{HashMap.get} and dereferences the resulting \texttt{null}, throwing an NPE. \\
Java/20 & Qwen returns the first tied pair; DeepSeek accumulates all ties into a list and returns the lexicographically smallest. \\
Java/21 & Qwen returns a fresh list; DeepSeek mutates the input list in place. \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================
% PHASE 2 METHODOLOGY
% =============================================================
\section{PHASE 2 METHODOLOGY}
\label{sec:phase2-method}

\subsection{The \texttt{BookScan} Class}

Phase~2 lifts three Phase~1 helpers (Java/18 \texttt{howManyTimes}, Java/23 \texttt{strlen}, Java/27 \texttt{flipCase}) into a single composite class \texttt{BookScan} that must:
\begin{itemize}
    \item count how many words of a requested length appear in a multi-line text and on which lines they appear (\texttt{scanByWordLength}),
    \item count how many times a requested whole word appears across lines, case-insensitively (\texttt{scanWord}),
    \item preserve the Phase~1 helper semantics so that \texttt{howManyTimes}, \texttt{strlen} and \texttt{flipCase} remain individually callable and individually testable.
\end{itemize}

The class lives at \texttt{Phase2/src/main/java/BookScan.java} and exposes two immutable result records and five public methods:

\begin{lstlisting}[language=Java, caption=Public surface of the final BookScan class]
public record ScanResult(
        int targetLength,
        int totalOccurrences,
        List<Integer> matchingLines,
        Map<Integer,Integer> occurrencesByLine,
        Map<Integer,List<String>> matchedWordsByLine) { }

public record WordSearchResult(
        String word,
        int totalOccurrences,
        List<Integer> matchingLines,
        Map<Integer,Integer> occurrencesByLine) { }

public ScanResult       scanByWordLength(String text, int targetLength);
public WordSearchResult scanWord       (String text, String word);
public int              howManyTimes   (String string, String substring);
public int              strlen         (String string);
public String           flipCase       (String string);
\end{lstlisting}

The tokenisation regex is \verb|[A-Za-z0-9]+(?:['-][A-Za-z0-9]+)*|, which keeps apostrophes and hyphens \emph{inside} a token (so that \texttt{can't} and \texttt{co-op} count as one word each) but rejects them as leading or trailing characters. Whole-word matching is implemented by canonicalising each line into a space-separated list of lowercase tokens and then padding the needle with spaces, so that partial matches inside longer words (e.g.\ ``echo'' inside ``echoic'') cannot fire.

\subsection{Maven + Surefire + JaCoCo + PITest Pipeline}

Phase~2 replaces the Phase~1 PowerShell+Python harness with a Maven build for the production code:
\begin{itemize}
    \item \textbf{JDK 21} (Temurin) and \textbf{Java release target 21} via \texttt{maven-compiler-plugin}.
    \item \textbf{JUnit 6} (\texttt{junit-jupiter} 6.0.3) on \texttt{maven-surefire-plugin} 3.5.3.
    \item \textbf{JaCoCo 0.8.12} via \texttt{jacoco-maven-plugin} (prepare-agent + report).
    \item \textbf{PITest 1.20.5} with \texttt{pitest-junit5-plugin 1.2.3} exposed through an opt-in Maven profile \texttt{mutation} so that the default \texttt{mvn clean verify} stays fast.
\end{itemize}

The PowerShell + Python driver is retained as a lightweight \emph{prompt-comparison harness}: \texttt{Phase2/scripts/python/run\_phase2\_prompt\_comparison.py}, wrapped by \texttt{Run-Phase2PromptComparison.ps1}, copies each candidate \texttt{BookScan.java} into an isolated work directory, compiles with \texttt{javac}, runs JUnit under the JaCoCo agent, renders a JaCoCo CSV from the resulting \texttt{jacoco.exec} and extracts branch coverage for the \texttt{BookScan} class. All raw artefacts (\texttt{compile.stdout}, \texttt{compile.stderr}, \texttt{junit.stdout}, \texttt{jacoco.exec}, \texttt{jacoco.csv} and the copied source files) are stored under \texttt{Phase2/results/artifacts/prompt-comparison/}.

GitHub Actions re-runs the entire Phase~2 build on every push (\texttt{.github/workflows/phase2-ci.yml}): \texttt{mvn clean verify}, the prompt-comparison harness, the PITest profile (best effort) and the polished Phase~2 artefact upload.

\subsection{Original-vs-Edited Prompt Strategies}

The headline experimental question of Phase~2 is: ``once the prompt has to specify a whole class rather than a single function, which matters more --- the underlying model, or the structure of the prompt itself?'' We answer it by running the same two models (Qwen2.5-Coder-1.5B and DeepSeek-Coder-1.3B) against two prompt strategies, plus a manually selected final implementation, all evaluated against the same JUnit suite.

\subsubsection{Original Combined Prompt}

The \emph{original combined prompt} simply concatenates the three HumanEval-X task descriptions and asks the model to build a class around them:

\begin{quote}\itshape
Create a Java class named \texttt{BookScan}. The class should determine how many times words of a given length appear in a text and on which lines they appear. The class must also contain methods related to HumanEval-X tasks \texttt{\#18 substring}, \texttt{\#23 string length} and \texttt{\#27 upper-lower case}. Return a single compilable Java file. Keep the implementation simple and self-contained.
\end{quote}

\subsubsection{Edited Combined Prompt}

The \emph{edited combined prompt} adds the integration contracts that the original prompt leaves implicit. Table~\ref{tab:prompt-edits} lists the eight added requirements; they are the contracts that the integration suite would otherwise have to discover by trial and error.

\begin{table}[H]
\centering
\caption{Integration contracts added in the edited combined prompt.}
\label{tab:prompt-edits}
\begin{tabular}{p{0.27\linewidth}p{0.65\linewidth}}
\toprule
\textbf{Topic} & \textbf{Added requirement} \\
\midrule
Line numbering    & one-based, each matching line listed at most once \\
Tokenisation      & apostrophes and hyphens stay inside a single token \\
Whole-word search & must not match inside a longer word \\
Case policy       & search is case-insensitive; uppercase-only queries canonicalised \\
Query hygiene     & trim the query, reject blank or multi-token queries \\
Invalid inputs    & null or blank text returns empty-result records \\
Result shape      & immutable \texttt{ScanResult} / \texttt{WordSearchResult} records \\
Helper reuse      & \texttt{howManyTimes}, \texttt{strlen}, \texttt{flipCase} remain callable with Phase 1 semantics \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Manually Selected Final Implementation}

After the prompt-comparison rounds, neither edited-prompt variant clears the full strengthened suite (each loses exactly one helper-hardening regression test, see Section~\ref{sec:phase2-results}). The repository therefore also stores a manually selected final implementation (\texttt{Phase2/src/main/java/BookScan.java}) that closes the last gap. This final implementation is the one that the Maven build, the JaCoCo report and the PITest profile target.

\subsection{Integration Test Suite}

The Phase~2 suite contains 12 integration tests (\texttt{BookScanIntegrationTest}) and 6 focused regression / hardening tests (\texttt{BookScanRegressionTest}), for a total of 18 tests shared by all five configurations. Tables~\ref{tab:int-tests} and \ref{tab:reg-tests} summarise them.

\begin{table}[H]
\centering
\caption{Integration tests in BookScanIntegrationTest.}
\label{tab:int-tests}
\begin{tabular}{p{0.42\linewidth}p{0.5\linewidth}}
\toprule
\textbf{Test method} & \textbf{Integration contract} \\
\midrule
\texttt{scanByWordLengthAggregatesCounts\-AndLinesAcrossText}     & multi-line aggregation and per-line matched words \\
\texttt{scanByWordLengthTreatsApostrophesAnd\-HyphensAsSingleWords}     & token-boundary preservation \\
\texttt{scanByWordLengthReturnsEmptyResult\-ForInvalidInputs}     & null / blank / non-positive length \\
\texttt{scanByWordLengthKeepsMatchingLines\-UniqueEvenWithManyHits}     & line-list uniqueness under repeated hits \\
\texttt{scanWordCountsWholeWordMatches\-IgnoringCaseAcrossLines}     & case-insensitive whole-word matching \\
\texttt{scanWordFindsTrimmedQueriesNextTo\-Punctuation}     & trimmed queries, punctuation handling \\
\texttt{scanWordRejectsBlankOrMultiTokenQueries}     & query validation (blank, multi-token) \\
\texttt{scanWordReturnsEmptyResultForNullInputs\-AndBlankTexts}     & null / blank inputs produce stable empty results \\
\texttt{scanWordDoesNotMatchInsideLongerWords}     & partial-match rejection \\
\texttt{scanWordCanonicalizesUppercaseQueries\-BeforeWholeWordMatching}     & uppercase queries normalised via \texttt{flipCase} \\
\texttt{scanWordHandlesAlphanumericWholeWordQueries}     & alphanumeric whole-word tokens \\
\texttt{scanWordNormalizesMixedCaseTokens\-WithoutFlipArtifacts}     & mixed-case normalisation remains stable \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Regression tests in BookScanRegressionTest.}
\label{tab:reg-tests}
\begin{tabular}{p{0.42\linewidth}p{0.5\linewidth}}
\toprule
\textbf{Test method} & \textbf{Phase 1 helper under test} \\
\midrule
\texttt{howManyTimesCountsOverlappingSubstrings}             & Java/18 overlap semantics \\
\texttt{howManyTimesReturnsZeroForEmpty\-NullOrOversizedNeedles}             & Java/18 guards on blank / oversized needles \\
\texttt{flipCasePreservesSymbolsWhile\-TogglingLetters}             & Java/27 case flip on symbols and digits \\
\texttt{strlenThrowsOnNullAndReturns\-LengthOtherwise}             & Java/23 null contract and length \\
\texttt{tokenizeWordsReturnsFreshMutable\-EmptyListForNullInput}             & helper hardening for null tokenisation \\
\texttt{privateCanonicalizeWordRejectsBlankTokens}             & helper hardening for blank-token collapse \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Black-Box Assessment for \texttt{BookScan}}

Each public method of \texttt{BookScan} has its own equivalence-partitioning document under \texttt{Phase2/docs/analysis/black\_box\_assessment.md}. The document enumerates valid classes (typical multi-line texts, repeated hits on the same line, apostrophe/hyphen tokens), invalid classes (null / blank text, non-positive target length, blank / multi-token query) and boundary conditions (empty matched-line list, single-token line, exact target length). Every public class is mapped to at least one executed JUnit method, and the mapping is reproduced as a separate table inside the document.

% =============================================================
% PHASE 2 TECHNICAL CHALLENGES
% =============================================================
\section{PHASE 2 TECHNICAL CHALLENGES AND SOLUTIONS}
\label{sec:phase2-challenges}

\subsection{Unicode Workspace Path Issues}

The development workspace lives under a path containing the Turkish character \emph{\.{I}}: \verb|D:\Indirilenler\BLG_475E_Term_Project\|. The Maven build originally placed the JaCoCo \texttt{destFile} and the Maven local repository under that path, which produced corrupted byte streams in \texttt{jacoco.exec} and intermittent resolver failures.

\subsubsection{Solution}

The Maven \texttt{jacoco-maven-plugin} configuration was updated to redirect both \texttt{destFile} and \texttt{dataFile} to the system tmpdir:

\begin{lstlisting}[language=XML, caption=JaCoCo plugin configuration in Phase2/pom.xml]
<plugin>
  <groupId>org.jacoco</groupId>
  <artifactId>jacoco-maven-plugin</artifactId>
  <version>${jacoco.version}</version>
  <configuration>
    <destFile>${java.io.tmpdir}/blg475e-${project.artifactId}-jacoco.exec</destFile>
    <dataFile>${java.io.tmpdir}/blg475e-${project.artifactId}-jacoco.exec</dataFile>
  </configuration>
  <!-- prepare-agent + report executions -->
</plugin>
\end{lstlisting}

The prompt-comparison harness was likewise updated to use a relative \texttt{jacoco.exec} next to the per-task work directory, and the Maven local repository was pinned to a workspace-local \texttt{.m2} folder via \texttt{-Dmaven.repo.local}, which is in turn excluded from version control.

\subsection{JaCoCo / PITest Coexistence}

PITest also instruments the bytecode, and when both JaCoCo's \texttt{prepare-agent} and PITest are active in the same Maven invocation the two tools sometimes produce conflicting class definitions. Running the mutation profile on a clean machine surfaced this as a classpath error.

\subsubsection{Solution}

The Phase~2 mutation profile sets \texttt{<jacoco.skip>true</jacoco.skip>} so that JaCoCo's \texttt{prepare-agent} does not fire when the user explicitly asks for a mutation run via \texttt{mvn -P mutation test}. The default \texttt{mvn clean verify} pipeline keeps JaCoCo enabled, which is what the GitHub Actions workflow uses for branch coverage.

\subsection{Original Prompt Failure Modes}

The original combined prompt produced four distinct defect classes per model on the JUnit suite. Table~\ref{tab:failure-modes} lists them; every defect class is an integration-level contract that is missing from the original prompt and that would have been invisible at the single-function Phase~1 level.

\begin{table}[H]
\centering
\caption{Original combined prompt: defect classes observed on the JUnit suite.}
\label{tab:failure-modes}
\begin{tabular}{p{0.16\linewidth}p{0.78\linewidth}}
\toprule
\textbf{Model} & \textbf{Defect classes hit by the JUnit suite} \\
\midrule
Qwen     & zero-based / non-unique line numbers; raw space-splitting destroys \texttt{can't} / \texttt{co-op}; case-sensitive substring search; missing canonicalisation for uppercase or alphanumeric queries; missing helper extraction for the final hardening checks. \\
DeepSeek & punctuation stripping changes token identity; substring matching inside longer words; over-counting in case-insensitive search; weak handling of punctuation around trimmed queries; alphanumeric over-counting; missing helper extraction for the final hardening checks. \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================
% PHASE 2 RESULTS
% =============================================================
\section{PHASE 2 RESULTS}
\label{sec:phase2-results}

\subsection{Prompt-Comparison Outcomes}

Table~\ref{tab:phase2-cmp} aggregates the raw CSV in \texttt{Phase2/results/prompt\_comparison\_results.csv}. The original prompt lets both models compile but produces significant JUnit failures; the edited prompt removes all public-integration failures but still leaves one helper-hardening regression in each model; the manually selected final implementation closes that gap and reaches full coverage.

\begin{table}[H]
\centering
\caption{Prompt-comparison results. Coverage is reported for the BookScan class only.}
\label{tab:phase2-cmp}
\begin{tabular}{llcr}
\toprule
\textbf{Strategy} & \textbf{Model} & \textbf{Tests passed} & \textbf{Branch coverage} \\
\midrule
original-combined & Qwen     & 6 / 18  & n/a \\
original-combined & DeepSeek & 8 / 18  & n/a \\
edited-combined   & Qwen     & 17 / 18 & n/a \\
edited-combined   & DeepSeek & 17 / 18 & n/a \\
selected-final    & manual   & 18 / 18 & 72 / 72 = 100.00\,\% \\
\bottomrule
\end{tabular}
\end{table}

The headline finding is that the edited prompt removes all public-integration failures for both models, while switching between Qwen and DeepSeek inside a fixed prompt strategy moves the pass-rate by no more than two test cases. Once the integration contracts are explicit, prompt clarity does more work than model selection.

\subsection{Final BookScan Coverage}

The Maven JaCoCo CSV at \texttt{Phase2/target/site/jacoco/jacoco.csv} reports for the manually selected final implementation:
\begin{itemize}
    \item branch coverage $72 / 72 = 100.00\,\%$,
    \item line coverage $110 / 110 = 100.00\,\%$,
    \item cyclomatic-complexity-covered $51 / 51 = 100.00\,\%$.
\end{itemize}
No JaCoCo branch or line misses remain in the final Maven report.

\subsection{PITest Mutation Score}

Running the opt-in Maven profile \texttt{mutation} (\texttt{mvn -P mutation test}) under the ASCII-safe configuration described in Section~\ref{sec:phase2-challenges} yields:
\begin{itemize}
    \item total mutants generated by PITest: \textbf{93},
    \item killed: \textbf{79},
    \item survived: \textbf{14},
    \item mutation score: $79 / 93 = \textbf{84.95\,\%}$,
    \item mutated-line coverage: $110 / 110 = 100.00\,\%$.
\end{itemize}

The 14 surviving mutants are concentrated on equivalent or defensive helper branches: 6 in \texttt{canonicalizeWord} (equivalent normalisation paths), 3 in \texttt{scanByWordLength} (defensive blank-input guard), 2 in \texttt{howManyTimes} (defensive behaviour), 1 each in \texttt{scanWord}, \texttt{tokenizeWords} and \texttt{flipCase}. The full breakdown lives in \texttt{Phase2/docs/analysis/mutation\_assessment.md}.

\subsection{Helper-Hardening Regression Closure}

Two of the six regression tests are specifically designed to close the last private-helper coverage gap that both edited-prompt variants leave open:
\begin{itemize}
    \item \texttt{tokenizeWordsReturnsFreshMutableEmptyListForNullInput} hardens the null-input behaviour of the tokenisation helper so that callers can mutate the returned list without affecting future calls.
    \item \texttt{privateCanonicalizeWordRejectsBlankTokens} pins down the blank-token normalisation rule that both edited-prompt variants miss; this is the test that distinguishes the manually selected final implementation from the two edited-prompt variants.
\end{itemize}

% =============================================================
% DISCUSSION
% =============================================================
\section{DISCUSSION}
\label{sec:discussion}

\subsection{Phase 1 versus Phase 2 Lessons}

The two phases tell a consistent story. In Phase~1, where each prompt is a single function, the dataset's reference test plus the equivalence-class extension already cover most of the meaningful behaviour, and the choice of model determines mostly defensive coding style. In Phase~2, where the prompt has to specify an integrated class, the dataset reference test no longer exists, the integration contracts are not stated by the prompt by default, and the choice of model is dwarfed by the choice of prompt: both models reach the same $\sim\!\!94\,\%$ pass rate under the edited prompt, even though under the original prompt they sat at $\sim\!\!33\!-\!\!44\,\%$.

\subsection{Prompt Engineering Outweighs Model Selection (at the Integration Level)}

The pattern that the data forces on us in Phase~2 is precise. Going from the original prompt to the edited prompt closes 11 / 18 (Qwen) and 9 / 18 (DeepSeek) tests; switching from one model to the other inside a fixed prompt closes only 0--2 tests. This is consistent with the recent literature on LLM unit-test generation \cite{metatestgen,yang2024,panta2024,lit_review}, where explicit specifications repeatedly outperform model upsizing.

\subsection{Hand-Crafted versus Automated Mutation Testing}

Phase~1 forbids automated mutation tooling, so the hand-crafted \texttt{improvedMutation\ldots} guards are an executable spec for the operator-level mutations the suite is supposed to catch. Phase~2 uses PITest in addition, which generates mutants automatically and removes the human-curation bias from the mutation set. The two perspectives are complementary: PITest discovers mutants we did not think of (and produces an 84.95\,\% kill rate that we now have to defend), while the hand-crafted guards force us to articulate \emph{why} a particular mutation should be killed, which makes the suite easier to maintain.

\subsection{Threats to Validity}

\begin{itemize}
    \item \textbf{Internal validity}: local-model non-determinism. Mitigated by pinning the sampling seed and the model checkpoints, and by re-running the entire pipeline under GitHub Actions.
    \item \textbf{External validity}: HumanEval-X is a corpus of single-function algorithmic puzzles, and \texttt{BookScan} is a single composite class rather than a full Java system. The headline numbers should therefore be read as ``what does this LLM look like on bite-sized Java tasks and on one composite class derived from them'' rather than ``what would this LLM look like in production''.
    \item \textbf{Construct validity}: branch coverage and mutation kill are proxies for test quality. We use both, and we report PITest as the automated counterpart to the hand-crafted Phase~1 guards.
\end{itemize}

\subsection{Future Work}

Two extensions would tighten the project further. First, sweeping the sampling seed across both models and reporting confidence intervals on the prompt-comparison delta would distinguish ``Qwen and DeepSeek are statistically different on the original prompt'' from ``the difference is within sampling noise''. Second, replacing the manually selected final implementation with an LLM-driven repair loop targeted at the surviving PITest mutants would close the loop that Phase~2 deliberately leaves open: today the final implementation is hand-curated, and a fully agentic version of the same workflow could re-issue the failing test as a refactoring prompt.

% =============================================================
% LITERATURE REVIEW
% =============================================================
\section{LITERATURE REVIEW}
\label{sec:literature}

The literature set was selected to cover five complementary perspectives on LLM-driven test generation, all published within the last three years (2023--2026): an early end-to-end tool paper, an industrial deployment study, a broad empirical evaluation of open-source LLMs, a hybrid coverage-driven test-generation technique and a recent systematic review. The selection was performed by hand using Google Scholar and IEEE Xplore; no LLM was used to surface or summarise the papers.

\textbf{ChatUniTest (Xie et al., 2023)} \cite{chatunitest} is an early reference point for LLM-based unit-test generation. Its main contribution is wrapping the model inside a generation-validation-repair loop. The paper argues that raw generations are often incomplete or syntactically broken, so validation and repair are necessary rather than optional. This motivates our normalisation plus repair loop in Phase~1: we did not accept generations that looked plausible, we accepted them only after they compiled and passed the dataset base test, and we extended the same instinct to the prompt-comparison harness in Phase~2.

\textbf{Automated Unit Test Improvement using LLMs at Meta (Alshahwan et al., 2024)} \cite{metatestgen} shifts the problem from generating tests from scratch to improving existing human-written tests. Its most important methodological lesson is that model output is accepted only after it passes build, execution, flakiness and coverage-gain filters. Our pipeline uses the same instinct: a generation is accepted only if it compiles, passes the dataset base test (Phase~1) or the integration suite (Phase~2) and produces measurable coverage under JaCoCo.

\textbf{On the Evaluation of LLMs in Unit Test Generation (Yang et al., 2024)} \cite{yang2024} is a direct empirical comparison of multiple open-source LLMs on Java unit-test generation, with an explicit prompt-structure axis. Two findings are relevant for our work: prompt structure materially affects compilation and coverage outcomes, and open-source models can be competitive but still need additional engineering. Our own measured results mirror this exactly: under the original combined prompt both Qwen and DeepSeek sit between 33\,\% and 45\,\% pass-rate; under the edited combined prompt both reach 94\,\%.

\textbf{LLM Test Generation via Iterative Hybrid Program Analysis / Panta (Gu et al., 2025; accepted to ICSE 2026)} \cite{panta2024} pushes beyond prompt tuning by combining LLM generation with static control-flow analysis and dynamic coverage feedback. The paper targets the specific weakness that also appears in our project: coverage gaps on branch-heavy code. Our improved-test step in Phase~1 and our PITest profile in Phase~2 are simpler instances of the same philosophy.

\textbf{Test case generation using LLMs: a Systematic Literature Review (Tasarsu, Tokmak and Catal, 2026)} \cite{lit_review} synthesises 38 peer-reviewed studies from 2020--2025. Its findings confirm patterns that are visible in our project: coverage remains the dominant evaluation metric, post-processing and integration logic are common, and maintainability / robustness are still weaker than simple coverage reporting. We therefore complement coverage with hand-crafted mutation guards in Phase~1 and with automated PITest in Phase~2, and we report all three numbers together.

% =============================================================
% CONCLUSION
% =============================================================
\section{CONCLUSION}
\label{sec:conclusion}

The combined Phase~1 + Phase~2 submission shows that two small open-weight code-LLMs (\texttt{Qwen2.5-Coder-1.5B-Instruct} and \texttt{DeepSeek-Coder-1.3B-Instruct}) can drive a reproducible Java evaluation pipeline when they are surrounded by normalisation, repair, coverage and mutation-based guardrails. On 30 HumanEval-X Java prompts both models reach 30 / 30 base-test success after at most one logged refactoring round; the improved suites lift aggregate branch coverage from 96.09\,\% / 98.46\,\% to 98.44\,\% / 100.00\,\%; every (task, model) pair carries at least one hand-crafted mutation guard.

Phase~2 lifts the helpers behind Java/18, Java/23 and Java/27 into a composite \texttt{BookScan} class and runs the same two models against an original combined prompt, an edited combined prompt and a manually selected final implementation under a Maven build with Surefire, JaCoCo and PITest. The original prompt produces 6 / 18 (Qwen) and 8 / 18 (DeepSeek) test passes; the edited prompt lifts both models to 17 / 18; the manually selected final implementation passes 18 / 18, reaches 100\,\% branch and 100\,\% line coverage and records an 84.95\,\% PITest mutation score. The most important Phase~2 lesson is that, at the integration level, prompt clarity does more work than model selection: explicit integration contracts close 9--11 tests, while switching between the two models closes at most two.

The combination of branch coverage (objective but blunt), hand-crafted mutation guards (targeted but human-curated) and PITest mutation analysis (automated but mechanical) gives three independent angles on test quality, and we report all three side by side because no single metric is sufficient on its own. The repository, including all interaction logs, scripts, CI workflows and raw artefacts, is publicly available under the URL listed in the acknowledgement so that every figure in this report can be reproduced from a clean checkout.

% =============================================================
% ACKNOWLEDGEMENT
% =============================================================
\section*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{section}{ACKNOWLEDGEMENT}

The source repository, including the prompt-comparison harness, the Maven build, the PITest profile, the GitHub Actions workflow and the raw JaCoCo artefacts, is available at \url{https://github.com/mustafaerenkoc44/BLG-475E-Term-Project}. The two-person group split the project workload along two complementary tracks; both authors contributed equally and continuously cross-reviewed each other's deliverables before they were merged. The same split applied to both Phase~1 and Phase~2.

\textbf{Mustafa Eren KO\c{C}} (150190805) led the \emph{engineering and automation} track: the repository scaffolding, the GitHub Actions CI workflows, the PowerShell + Python~3.11 driver layer, the local \texttt{llama.cpp} execution pipeline, the dataset-to-JUnit adapters, the JaCoCo automation, the Maven and PITest configuration, the \texttt{BookScan} reference implementation and helper hardening, the prompt-comparison harness and the Git commit discipline.

\textbf{Onat Bar{\i}\c{s} ERCAN} (150210075) led the \emph{quality and analysis} track: the 30-prompt selection rationale and easy / moderate / hard categorisation, the per-task equivalence-partitioning and boundary-value documents, the test-smell audit, the hand-crafted mutation-operator catalogue and the \texttt{improvedMutation\ldots} JUnit method authoring, the \texttt{BookScan} black-box assessment, the original-versus-edited prompt-strategy design, the failure-mode classification, the five-paper literature review and the term-project manuscript.

% =============================================================
% REFERENCES
% =============================================================
\begin{thebibliography}{9}

\bibitem{humaneval}
M. Chen, J. Tworek, H. Jun, et al.
\newblock Evaluating Large Language Models Trained on Code.
\newblock \emph{arXiv preprint arXiv:2107.03374}, 2021.
\newblock URL: \url{https://arxiv.org/abs/2107.03374}.

\bibitem{chatunitest}
Z. Xie, Y. Chen, C. Zhi, S. Deng, and J. Yin.
\newblock {ChatUniTest}: a {ChatGPT}-based automated unit test generation tool.
\newblock \emph{CoRR}, abs/2305.04764, 2023.
\newblock DOI: 10.48550/arXiv.2305.04764.

\bibitem{metatestgen}
N. Alshahwan, J. Chheda, A. Finogenova, B. Gokkaya, M. Harman, I. Harper, A. Marginean, S. Sengupta, and E. Wang.
\newblock Automated Unit Test Improvement using Large Language Models at Meta.
\newblock In \emph{Companion Proceedings of the 32nd ACM International Conference on the Foundations of Software Engineering (FSE Companion)}, pp.\ 185--196, 2024.
\newblock DOI: 10.1145/3663529.3663839.

\bibitem{yang2024}
L. Yang, C. Yang, S. Gao, W. Wang, B. Wang, Q. Zhu, X. Chu, J. Zhou, G. Liang, Q. Wang, and J. Chen.
\newblock On the Evaluation of Large Language Models in Unit Test Generation.
\newblock In \emph{Proceedings of the 39th IEEE/ACM International Conference on Automated Software Engineering (ASE)}, pp.\ 987--999, 2024.
\newblock DOI: 10.1145/3691620.3695529.

\bibitem{panta2024}
S. Gu, N. Nashid, and A. Mesbah.
\newblock {LLM} Test Generation via Iterative Hybrid Program Analysis.
\newblock \emph{CoRR}, abs/2503.13580, 2025. Accepted to ICSE 2026.
\newblock DOI: 10.48550/arXiv.2503.13580.

\bibitem{lit_review}
M. Tasarsu, A. V. Tokmak, and C. Catal.
\newblock Test case generation using large language models: a systematic literature review.
\newblock \emph{Cluster Computing}, 29(4), Springer, 2026.
\newblock DOI: 10.1007/s10586-026-06021-z.

\end{thebibliography}

% =============================================================
% APPENDIX
% =============================================================
\appendix
\section{Selected HumanEval-X Java Prompts}
\label{app:prompts}

The 30 prompts selected for Phase~1, with their difficulty labels and Phase~2 dependency flag:

\begin{table}[H]
\centering
\caption{Phase 1 selected prompts (full list).}
\label{tab:prompts-full}
\begin{tabular}{llll}
\toprule
\textbf{Task} & \textbf{Method} & \textbf{Difficulty} & \textbf{Phase 2 dependency?} \\
\midrule
Java/2  & truncateNumber       & easy     & no \\
Java/3  & belowZero            & easy     & no \\
Java/9  & rollingMax           & easy     & no \\
Java/11 & stringXor            & easy     & no \\
Java/13 & greatestCommonDivisor& easy     & no \\
Java/14 & allPrefixes          & easy     & no \\
Java/22 & filterIntegers       & easy     & no \\
Java/23 & strlen               & easy     & \textbf{yes} \\
Java/24 & largestDivisor       & easy     & no \\
Java/27 & flipCase             & easy     & \textbf{yes} \\
\midrule
Java/0  & hasCloseElements     & moderate & no \\
Java/4  & meanAbsoluteDeviation& moderate & no \\
Java/5  & intersperse          & moderate & no \\
Java/8  & sumProduct           & moderate & no \\
Java/15 & stringSequence       & moderate & no \\
Java/16 & countDistinctChars   & moderate & no \\
Java/18 & howManyTimes         & moderate & \textbf{yes} \\
Java/19 & sortNumbers          & moderate & no \\
Java/25 & factorize            & moderate & no \\
Java/29 & filterByPrefix       & moderate & no \\
\midrule
Java/1  & separateParenGroups  & hard     & no \\
Java/6  & parseNestedParens    & hard     & no \\
Java/7  & filterBySubstring    & hard     & no \\
Java/10 & isPalindrome         & hard     & no \\
Java/12 & longest              & hard     & no \\
Java/17 & parseMusic           & hard     & no \\
Java/20 & findClosestElements  & hard     & no \\
Java/21 & rescaleToUnit        & hard     & no \\
Java/31 & isPrime              & hard     & no \\
Java/39 & primeFib             & hard     & no \\
\bottomrule
\end{tabular}
\end{table}

\section{Build and Reproduction Instructions}
\label{app:build}

\subsection{Prerequisites}

\begin{itemize}
    \item JDK 21 (Temurin recommended)
    \item Maven 3.9 or newer (for Phase 2 build)
    \item Python 3.11 (for the Phase 1 + Phase 2 driver scripts)
    \item PowerShell 7 (for the Phase 1 + Phase 2 PowerShell wrappers)
    \item \texttt{llama.cpp} runtime with the GGUF model files placed under \texttt{.tools/models/}
\end{itemize}

\subsection{Phase 1 Reproduction}

\begin{lstlisting}[language=bash, caption=Reproducing the Phase 1 coverage CSVs]
# from the repository root
python Phase1/scripts/python/run_base_coverage.py \
  --tasks-root Phase1/tasks \
  --results   Phase1/results/base_coverage_results.csv \
  --java      $JAVA_HOME/bin/java \
  --javac     $JAVA_HOME/bin/javac \
  --junit-console .tools/junit-platform-console-standalone-6.0.3.jar \
  --jacoco-agent  .tools/org.jacoco.agent-0.8.12-runtime.jar \
  --jacoco-cli    .tools/org.jacoco.cli-0.8.12-nodeps.jar
\end{lstlisting}

A second invocation with \verb|--test-stage improved --test-file-name DatasetImprovedTest.java| produces the improved-coverage CSV. The same flow is automated in \texttt{.github/workflows/phase1-ci.yml}.

\subsection{Phase 2 Reproduction}

\begin{lstlisting}[language=bash, caption=Reproducing the Phase 2 BookScan build and PITest report]
# from Phase2/
mvn -Dmaven.repo.local="$PWD/.m2" clean verify
mvn -Dmaven.repo.local="$PWD/.m2" -P mutation -DskipTests=false test
\end{lstlisting}

The first command runs the 18-test Surefire suite and writes the JaCoCo report to \texttt{target/site/jacoco/}. The second command runs PITest and writes the mutation report to \texttt{target/pit-reports/}. The same flow is automated in \texttt{.github/workflows/phase2-ci.yml}.

\subsection{Repository Layout}

\begin{verbatim}
BLG_475E_Term_Project/
|- Phase1/
|  |- data/selected_prompts.csv              # 30 prompts + difficulty
|  |- tasks/Java_<NNN>_<name>/               # per-task analysis
|  |  |- analysis/equivalence_classes.md     # black-box analysis
|  |  |- generated-code/<model>/Solution.java
|  |  |- generated-tests/base/<model>/DatasetBaseTest.java
|  |  '- generated-tests/improved/<model>/DatasetImprovedTest.java
|  |- logs/<model>/Java_<N>_<step>.md        # full prompt + response logs
|  |- results/base_coverage_results.csv      # JaCoCo base CSV
|  |- results/improved_coverage_results.csv  # JaCoCo improved CSV
|  '- docs/report/ieee/phase1_report.tex     # Phase 1 standalone report
|- Phase2/
|  |- src/main/java/BookScan.java            # final BookScan implementation
|  |- src/test/java/BookScanIntegrationTest.java
|  |- src/test/java/BookScanRegressionTest.java
|  |- pom.xml                                # Maven + JaCoCo + PITest
|  |- scripts/python/run_phase2_prompt_comparison.py
|  |- results/prompt_comparison_results.csv  # 5-row outcome CSV
|  |- target/site/jacoco/jacoco.csv          # Maven JaCoCo report
|  |- target/pit-reports/mutations.csv       # Maven PITest report
|  '- docs/report/ieee/phase2_report.tex     # this report
|- .github/workflows/phase1-ci.yml
|- .github/workflows/phase2-ci.yml
'- reports/                                  # polished PDF copies
\end{verbatim}

\end{document}
